Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
capitalize NumPy, SciPy

\paragraph{Setting up models and feeding them data.}
%
Models in scikit-learn, called \emph{estimators}, are objects
instantiated with all parameters that describe them, but with data. They
have a {\tt fit} method, that accepts an $(n \times p)$ data matrix,
$\mathbf{X}$ --numpy array or scipy sparse matrix--, where $n$ is the
number of samples, and $p$ the number of features--, and possibly a
quantity to predict, $\mathbf{y}$, also an array, 1D unless the
prediction is \emph{multi-output}, with floats for a regression task, as
in the wages prediction, or integers for classification, that is
predicting for each sample to which class it belongs. The data seldom
come in this form, and they must be adapted to be suitable for
consumption by estimators.

>>>>

\paragraph{Setting up models and feeding them data.}
%
Models in scikit-learn, called \emph{estimators}, are objects
instantiated with all parameters that describe them, but with data. They
have a {\tt fit} method, that accepts an $(n \times p)$ data matrix,
$\mathbf{X}$ --NumPy array or SciPy sparse matrix--, where $n$ is the
number of samples, and $p$ the number of features--, and possibly a
quantity to predict, $\mathbf{y}$, also an array, 1D unless the
prediction is \emph{multi-output}, with floats for a regression task, as
in the wages prediction, or integers for classification, that is
predicting for each sample to which class it belongs. The data seldom
come in this form, and they must be adapted to be suitable for
consumption by estimators.
